%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Clean, single-page LaTeX resume (no personal email/phone)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[paper=a4,fontsize=10.5pt]{scrartcl}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage[svgnames]{xcolor}
\usepackage[left=1.4cm,right=1.4cm,top=1.8cm,bottom=1.8cm]{geometry}
\usepackage{sectsty}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.5em, itemsep=0pt, topsep=2pt}
\sectionfont{\usefont{OT1}{phv}{b}{n}\sectionrule{0pt}{0pt}{-5pt}{3pt}}
\frenchspacing
\pagestyle{empty}

\newcommand{\MyName}[1]{\begin{center}\Huge\usefont{OT1}{ppl}{b}{n}#1\end{center}}
\newcommand{\PersonalEntry}[2]{\noindent\hangindent=2em\hangafter=0\textit{#1}\hspace{1.2em}#2\par}
\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}
\newcommand{\WorkEntry}[4]{\noindent\textbf{#1}\hfill\colorbox{White}{#2}\par\noindent\textit{#3}\par\small#4\normalsize\par}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\MyName{Kennedy "Ken" Johnson}
\PersonalEntry{Location}{St. Paul, MN}
\PersonalEntry{LinkedIn}{https://www.linkedin.com/in/kennedy-ken-johnson/}

\NewPart{Education}
\WorkEntry{University of Minnesota -- Twin Cities}{Fall 2021 -- Fall 2024}{B.S. in Data Science, GPA: 3.7}{Relevant coursework: Machine Learning, Databases, Algorithms, Statistics, Linear Algebra, Data Visualization.}

\NewPart{Experience}

\WorkEntry{Data Engineer}{Feb 2025 -- Present}{Travelers Insurance -- St. Paul, MN}{
\begin{itemize}
  \item Engineer and maintain environments and data pipelines using AWS, Snowflake, and Databricks on infrastructure team.
  \item Collaborate with cross-functional teams to support data workflows, platform upgrades, and efficient resource utilization.
  \item Design scalable ETL workflows and optimize data storage and compute performance for analytics workloads.
\end{itemize}}

\WorkEntry{Business Intelligence Intern -- Business Insights & Analytics LDP}{Summer 2024}{Travelers Insurance -- St. Paul, MN}{
\begin{itemize}
  \item Built automated model monitoring infrastructure using Snowflake, SQL, AWS, and Python.
  \item Developed a model health dashboard tracking performance metrics for hundreds of internal users.
  \item Detected a major production issue through new data quality pipelines, preventing model failure.
\end{itemize}}

\WorkEntry{Teaching Assistant -- Computer Systems & Linear Algebra}{Fall 2023 -- Spring 2024}{University of Minnesota -- Twin Cities}{
\begin{itemize}
  \item Led two lab sections (39 students total) teaching Python, C, and assembly-level computation.
  \item Taught a discussion section of 40 students on foundational linear algebra principles.
  \item Provided technical mentorship and grading support for numerical computing and systems courses.
\end{itemize}}

\WorkEntry{Network Operations & Systems Engineering Intern}{Summer 2022 & 2023}{Arvig -- Roseville, MN}{
\begin{itemize}
  \item Automated network inventory management using the NetBox API and Python Pandas.
  \item Integrated data across multiple systems, improving visibility for millions of dollars in assets.
\end{itemize}}

\NewPart{Projects & Achievements}
\WorkEntry{MinneMUDAC Data Science Competition}{March 2023}{First Place -- Novice Division}{
\begin{itemize}
  \item Presented statistical analysis and business recommendations for the Minnesota Twins to a panel of data scientists and executives.
  \item Led technical modeling and final presentation for a team of four, achieving top score among 15 teams.
\end{itemize}}

\WorkEntry{Gopher Metro (Student Project)}{Fall 2023 -- ongoing}{University of Minnesota}{
\begin{itemize}
  \item Developing a campus transportation web app integrating live bus data and route optimization.
\end{itemize}}

\NewPart{Technical Skills}
\noindent Python, SQL, AWS, Databricks, Snowflake, Pandas, NumPy, R, Git, Linux

\end{document}
